moduleoneanalysis

### 2023-09-20 module1/moduleoneanalysis.Rmd
changing regional scripts to english in excel file

drinkingwater   	What is the main source of drinking water for the members of your household?
cookingwater      What is the main source of water used by your\r\nhousehold for other purposes such as cooking and\r\nhandwashing?
farwatermins      How long does it take to go there, get water, and come\r\nback? 
toilet            What kind of toilet facility do members of your\r\nhousehold usually use?
house
stove
vehicle
houseown

>>>>

drinkingwater   	What is the main source of drinking water for the members of your household?
cookingwater      What is the main source of water used by your household for other purposes such as cooking and handwashing?
farwatermins      How long does it take to go there, get water, and come back? 
toilet            What kind of toilet facility do members of your nhousehold usually use?
house
stove
vehicle
houseown
